\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-07 paper.tex
Worked on the intro

\usepackage[utf8x]{inputenc}
\usepackage{cite}
\usepackage{graphicx}
\graphicspath{{figs/}}
\DeclareGraphicsExtensions{.pdf,.jpg,.png}

@@

\subsection{The LAAS deliberative layer}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\graphicspath{{figs/}}
\DeclareGraphicsExtensions{.pdf,.jpg,.png}

@@

\subsection{Towards the cognitive robot at LAAS}

Natural interaction and cooperation are the current (dare we say,
\emph{short-term}) targets for the human-robot interaction community. They are
keys to the broad class of \emph{interactive manipulation problems}: several
agents agree on a (more or less implicit) joint goal that requires some sort of
cooperation to be successfully achieved. This class of problems involves both
dialogue and manipulation and they are often not completely defined at
start-up: they require iterative and interactive resolution.

Over the last years we have focused our efforts on identifying the cognitive
prerequisites of these challenges, and giving them experimental reality on the
robots: what is required for a sentence like ``Let's dress the table together''
to be understood by the robot, correctly interpreted in the spatial and
temporal context of the interaction, and eventually transformed into a set of
actions?

We have chosen to tackle the challenge from several ends: human-aware
navigation and motion planning (\cite{...Mamoun}), situation assessment coupled
with motion planning (\cite{...}), projection of ``mightabilities'' that
anticipates what surrounding agents may do (\cite{Amit...}), and the design and
deployment of a pervasive \emph{knowledge-centric} software architecture.

We focus in this paper on that last item, to present what that means, and what
are the benefits and drawbacks.

\subsection{Deployment on robots}

While we do not present them here, the ideas and techniques pertaining to this
paper have been all implemented and tested on several robots (see previously
reported experiments in~\cite{Lemaignan2010, Ros2010b, Lemaignan2011a,
Warnier2012a}). Videos presenting some of these experimental results can also
be watched online at~\url{http://www.laas.fr/~slemaign}.

\subsection{Article overview}

We first describe with more details how the deliberative layer of our robots is
built and why this monolithic functional group enables what we call a
\emph{knowledge-oriented} architecture. The first section also introduce our
central knowledge management tool, the ORO server.

The next sections go over each of the facets of this deliberative layer: how
knowledge is produced asynchronously from geometric reasoning, how the robot
conducts grounded multi-modal interaction with humans, how knowledge is used by
decision-making components like the robot controller or the task planner, and
finally, how our knowledge-centric architecture enables the implementation of
specific internal cognitive processes.

We conclude the article with a discussion about the strenghts and weaknesses of
such a knowledge-oriented architecture, fron three perspectives: the architect,
the IA expert and the cognitician.

\section{The LAAS deliberative layer}
